\documentclass{article}

% 1 inch margins
\usepackage[margin=1in]{geometry}

% Link
\usepackage{hyperref}

% Prevent paragraph indentation
\usepackage{parskip}

% Page header
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{Jai Wargacki}
\rhead{CSCI-711-01 Global Illumination\\ Project Proposal}

\begin{document}
% Title -- A short (ideally) but catchy name for your project; essentially, a summary of what you're doing in a few words.
\textbf{Title:} Dash Cam Path Visualization

% Name(s) -- Your name (if you are working alone), or a list of the names of the members of the team (if working as a team) with an indication of who is the team leader.
\textbf{Name:} Jai Wargacki

% Class name and number -- CSCI-711, Global Illumination.
\textbf{Class:} CSCI-711, Global Illumination

% Project web site URL -- This is where you'll post all your project-related material (including your proposal).
\textbf{Project URL:} \url{https://cs.rit.edu/~jpw5681/cs711/Website/}

% Summary of the project -- A description of the 3D scene that is to be constructed, the aspect of the rendering pipeline that will be emphasized, and the means by which you plan on doing so.
\textbf{Summary:} The goal of this project is to create a visualization of a recorded dash cam path on a 3D map.
Additionally, when the user mouses over the path, a thumbnail of the video at that point will be displayed for the user to view.
This project will emphasize interactivity. The user is able to move the camera around the scene to view the path from different angles
as well as hover the mouse over the path to view the video at that point. This project will be accomplished by adding additional 3D elements to 
webGL elements provided by the Google Maps API. It is currently unclear what will be needed additionally to plot a smooth path on the map, and
display the video thumbnails over the route.

% Project objectives -- What are you trying to accomplish by working on this project?
\textbf{Objectives:} My motivation for this project is to create a visualization that can be integrated with my capstone project which 
is a dash cam video management software.

% System and software -- The computer hardware and software that you are planning to use to implement this project.
\textbf{System and Software:} This project will be implemented using webGL and make use of the Google Maps API for mapping. 
The project will be written in JavaScript and HTML and run in a web browser.
The project will be hosted at the same URL as listed above.

% Project components -- A breakdown of the pieces (e.g., a GUI, ray tracer modifications, etc.) of the project, with as many details as possible.
\textbf{Components:} The currently the only planned component of this project is the visualization itself which is a GUI. A possible other 
component for this project would be a data loader, depending on the expected/needed format of the data.

% Project responsibilities -- A detailed list of tasks (and who will do them, if a group project).
\textbf{Project Tasks:}
\begin{itemize}
    \item Loading 3D map
    \item Loading dash cam path
    \item Displaying correct portion of map based on path
    \item Displaying path on map
    \item Displaying video thumbnails on path on mouse over
\end{itemize}

% Project timeline -- A list of milestones (e.g., initial design, skeletal prototype, first running code, etc.) along with an estimate of when you expect to achieve each one. 
% (Dates here will, obviously, be estimates; they're not cast in stone, but rather in sand, as they will very likely slip during your work.)
\textbf{Project Timeline:}
\begin{itemize}
    \item Week 4: Setting up project, loading 3D map
    \item Week 5: Loading dash cam data
    \item Week 6: Creating path from dash cam data (not yet displayed on map)
    \item Week 7: Displaying correct portion of map based on path coordinates
    \item Week 8: Displaying path on map
    \item Week 9: Displaying path on map (cont.)
    \item Week 10: Displaying video thumbnails on path on mouse over
    \item Week 11: Displaying video thumbnails on path on mouse over (cont.)
    \item Week 12: Improvements to UI and user experience
    \item Week 13: Improvements to UI and user experience (cont.)
    \item Week 14: Finishing touches
\end{itemize}

% Final presentation -- An indication of how you plan to demonstrate or present the project during the project presentation sessiojn at the end of the term.
\textbf{Final Presentation:} The project will be demonstrated by demoing the visualization on a variety of dash cam routes.

\end{document}